\chapter{Results and Discussion}

\section{Introduction}

This chapter analyzes the outcomes of the RM project against the objectives and requirements defined in previous chapters. It presents achieved results, discusses their operational value, and identifies current limitations and improvement perspectives.

\section{Evaluation Framework}

Project evaluation is based on three dimensions:

\begin{enumerate}
\item \textbf{Functional completion}: coverage of required business capabilities.
\item \textbf{Operational contribution}: improvement of intervention management practices.
\item \textbf{Technical quality}: consistency, traceability, and maintainability of the implemented solution.
\end{enumerate}

\section{Achieved Functional Results}

\subsection{Lifecycle Digitization}

The intervention workflow is now managed through a structured digital process from request creation to archival. This result directly addresses the initial need for process standardization.

\subsection{Role-Based Collaboration}

The platform operationalizes role responsibilities for technicians, supervisors, coordinators, and administrators. This improves accountability and clarifies decision authority at each workflow step.

\subsection{Validation and Traceability}

Approval and rejection mechanisms with status history provide auditable intervention follow-up. This significantly strengthens quality governance.

\subsection{Evidence and Reporting}

Evidence attachment and report generation capabilities improve project documentation quality and facilitate communication with stakeholders.

\section{Discussion of Results}

\subsection{Alignment with Initial Objectives}

The implemented system satisfies the core project objective: delivering an integrated intervention management platform. Key objective alignment is observed as follows:

\begin{itemize}
\item process digitalization was achieved through structured data capture and workflow control,
\item visibility improved through status-driven supervision,
\item reporting effort was reduced via automated output generation,
\item and coordination quality improved through shared process states.
\end{itemize}

\subsection{Operational Impact}

From an organizational perspective, the main contributions are:

\begin{itemize}
\item reduced fragmentation of intervention information,
\item improved consistency of field data,
\item clearer validation cycles,
\item and better readiness for managerial monitoring.
\end{itemize}

\subsection{Technical Impact}

From an engineering perspective, the architecture supports incremental evolution and module extension. The separation between requirement specification, design, and implementation improved development clarity and maintainability.

\section{Project Metrics and Delivery Summary}

\begin{table}[H]
\centering
\caption{Project Delivery Indicators}
\label{tab:project_delivery_indicators}
\begin{tabularx}{\textwidth}{|l|r|}
\hline
\textbf{Indicator} & \textbf{Value} \\
\hline
Development iterations (sprints) & 5 \\
\hline
Functional blocks delivered & 4 \\
\hline
Primary actor profiles supported & 4 \\
\hline
Core workflow stages covered & 5 \\
\hline
Major reporting capability implemented & 1 \\
\hline
\end{tabularx}
\end{table}

These indicators confirm consistent progression from foundation setup to operational and analytical features.

\section{Limitations}

Despite the achieved results, several limitations remain:

\begin{itemize}
\item performance benchmarking can be extended with larger production-like workloads,
\item advanced analytics and predictive reporting are not yet integrated,
\item integration with external enterprise systems remains limited,
\item and longitudinal user-adoption measurements require longer observation periods.
\end{itemize}

\section{Improvement Perspectives}

The following extensions are relevant for future iterations:

\begin{enumerate}
\item advanced KPI dashboards and trend analytics,
\item richer notification and escalation mechanisms,
\item expanded interoperability with external platforms,
\item and deeper automation of quality-control checks.
\end{enumerate}

\section{Chapter Conclusion}

The RM project produced a coherent and operationally relevant solution for intervention management. Results demonstrate substantial progress in workflow structuring, traceability, and reporting quality. The discussion also highlights realistic improvement paths to further strengthen organizational value and technical maturity.
