\chapter{General Presentation}

\section{Introduction}

This chapter presents the organizational and operational context of the project. It introduces Africom Services, clarifies the business environment in which the internship was conducted, formulates the project problematic, and defines the objectives that guided the development of the RM platform.

\section{Company Overview}

\subsection{Company Identity}

Africom Services is a Tunisian company created in January 2005 by experienced professionals in telecommunications. The company positions itself as an engineering and maintenance actor focused on communication infrastructure reliability and modernization.

\subsection{Main Activity Domains}

Africom Services operates across complementary domains:

\begin{itemize}
\item \textbf{Telecommunications}: installation and testing of transmission and multiplexing equipment.
\item \textbf{Radio-electric networks}: deployment of microwave links and related infrastructure.
\item \textbf{Fiber optics}: implementation of high-bandwidth connectivity solutions.
\item \textbf{Maintenance}: preventive and corrective interventions on communication systems.
\item \textbf{Electronic security}: GPS-based fleet monitoring and real-time tracking solutions.
\item \textbf{Energy and IT integration}: adapted solutions for telecom infrastructure and information systems.
\end{itemize}

\subsection{Positioning and Partnerships}

Africom Services supports telecom operators, private enterprises, and public institutions in infrastructure projects. Its partnership with Telecom Canada reinforces its technical capacity in private networks, wireless communication, and digital infrastructure deployment.

\subsection{Strategic Orientation}

The company strategy is based on four principles:

\begin{enumerate}
\item \textbf{Innovation}: integration of modern digital tools and operational applications.
\item \textbf{Quality}: alignment with recognized technical standards.
\item \textbf{Client proximity}: adaptation of services to project-specific needs.
\item \textbf{Responsibility}: attention to ethics, safety, and environmental constraints.
\end{enumerate}

\section{Project Context}

\subsection{Operational Setting}

The project is situated in field intervention management for IT and telecom equipment. Interventions involve planning, assignment, on-site execution, quality validation, and final reporting. These activities are distributed across multiple stakeholders and geographic locations, which increases coordination complexity.

\subsection{Business Need}

The host company required a unified information system capable of:

\begin{itemize}
\item structuring intervention workflows,
\item improving execution traceability,
\item reducing report production delays,
\item and standardizing data capture quality.
\end{itemize}

This need led to the development of \textbf{RM (Report Manager)}, a platform combining web and mobile interfaces to manage interventions end-to-end.

\section{Problematic}

Before this project, intervention management faced recurring limitations:

\begin{itemize}
\item fragmented operational information,
\item inconsistent field data quality,
\item limited real-time visibility for supervisors,
\item heavy manual effort for report consolidation,
\item and delayed validation cycles.
\end{itemize}

The central problematic can therefore be expressed as follows:

\begin{quote}
How can Africom Services implement a robust digital platform that standardizes intervention processes, strengthens traceability, and improves operational efficiency while supporting collaborative decision-making?
\end{quote}

\section{Project Objectives}

\subsection{General Objective}

Design and implement a scalable intervention management platform that supports planning, execution, validation, and reporting for IT equipment operations.

\subsection{Specific Objectives}

\begin{enumerate}
\item Define a coherent role-based workflow for technicians, supervisors, coordinators, and administrators.
\item Formalize intervention requirements and constraints in a structured specification.
\item Design a maintainable system architecture for web and mobile usage.
\item Implement core functional modules for intervention management and reporting.
\item Evaluate technical and operational outcomes through measurable project results.
\end{enumerate}

\section{Chapter Conclusion}

This chapter established the organizational context and strategic motivation of the project. It clarified the business need, formalized the problematic, and defined objectives that guide the rest of the report. The next chapter develops the analysis phase and requirements specification that translate these objectives into actionable system requirements.
