\cleardoublepage
\thispagestyle{empty}

\begin{center}

{\Large\textit{DEDICATION}}

\vspace{1cm}

\textbf{To my dear parents, the greatest blessing in my life,}

\vspace{0.3cm}

Since some debts can never truly be repaid, no matter how much time passes, I dedicate this work to my beloved parents.  
You are the foundation of everything I have achieved and the source of the values that guide my life.  
Your unconditional love, sacrifices, patience, and constant encouragement have allowed me to move forward even in the most difficult moments.  
Every success I achieve carries a part of your effort and your devotion.  
I hope that this accomplishment makes you proud and reflects, even in a small way, the immense love and support you have always given me.

\vspace{0.6cm}

\textbf{To my dear sister,}

\vspace{0.3cm}

Words are not enough to express the affection and gratitude I feel for you.  
Your kindness, encouragement, and constant presence have always been a source of strength in my life.  
Through both joyful and challenging moments, you have always stood by my side with sincerity and support.  
With all my love and appreciation, I dedicate this work to you and wish you a life filled with happiness, success, and fulfillment.

\vspace{0.6cm}

\textbf{To my closest friends --- EL ``Cliqua'',}

\vspace{0.3cm}

Calling you simply friends would be an understatement.  
You are a second family who have filled my life with unforgettable memories, laughter, and support.  
Through the ups and downs of this journey, your presence made every challenge easier and every success more meaningful.  
Thank you for the encouragement, the motivation, and the countless moments that made these years truly special.  
This work is also yours.

\vspace{0.6cm}

\textbf{To Faten,}

\vspace{0.3cm}

Your pure soul and kind heart have always been a safe space where I can truly be myself.  
You have a unique way of making me believe in myself and see things with more clarity and confidence.  
Your presence in my life brings calm, balance, and a steadiness that helps me move forward with a clearer vision.  
For the inner peace and strength you bring into my life, I dedicate this work to you with sincere affection.

\vspace{0.8cm}

\textit{With gratitude and love}

\end{center}

\cleardoublepage