
\cleardoublepage
\thispagestyle{empty}

\begin{center}

{\Large\textit{ACKNOWLEDGEMENTS}}

\vspace{1cm}

\textbf{First and foremost, to God,}

\vspace{0.3cm}

I would like to express my deepest gratitude to God for granting me the strength, patience, and perseverance needed to complete this work.  
Throughout this journey, His guidance has helped me overcome challenges and continue moving forward with determination.  
Without these blessings, the completion of this project would not have been possible.

\vspace{0.6cm}

\textbf{To my academic supervisor Maroua BELKNENI,}

\vspace{0.3cm}

I would like to express my sincere appreciation to my academic supervisor for their guidance, valuable advice, and continuous support throughout the realization of this project.  
Their insights and encouragement played an essential role in shaping this work and helping me overcome many challenges during this journey.

\vspace{0.6cm}

\textbf{To my professional supervisor Nader KESSENTINI,}

\vspace{0.3cm}

I would like to extend my sincere thanks to my professional supervisor for giving me the opportunity to carry out my final year project within the company.  
Their trust, availability, and practical guidance allowed me to better understand the professional environment and apply my academic knowledge to real-world challenges.

\vspace{0.6cm}

\textbf{To the team at Africom Services,}

\vspace{0.3cm}

I would also like to warmly thank the entire team at \textbf{Africom Services} for their welcome, collaboration, and willingness to share their knowledge.  
Working alongside such a supportive and professional team made this experience both enriching and inspiring, and it contributed greatly to my personal and professional growth.

\vspace{0.8cm}

\textit{My sincere gratitude to everyone who contributed, directly or indirectly, to the realization of this work.}

\end{center}

\cleardoublepage